{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
ux sprint overview section

\section{Introduction} %%%

@@

The heart of our investigation will be a large-scale user study
that measures how effectively users are able to complete
basic web browsing tasks in the presence of a censor.
We will place users in a controlled network environment
that simulates the kind of censorship conditions that many
users around the world face daily.
We will be testing specific circumvention software---namely,
Tor Browser---though our larger contribution is to establish
a usability testing methodology for the evaluation
of this kind of software.

@@

\indent \indent Censorship and other information controls
are widespread on the Internet and increasing in prevalence.
Since 2011, Freedom House has published a yearly report
on the state of Internet freedom in dozens of countries.
The 2014 report~\cite{freedom-on-the-net-2014} observes
an overall decrease in freedom worldwide,
with 36 of 65 surveyed countries decreasing in their freedom rating
since 2013 (only 12 countries had an increase).

To escape restrictive networks and communicate more freely,
users turn to a variety of censorship circumvention technologies.
What tools are necessary depends greatly on the specifics of
a particular censor;
they range from simple one-hop proxies and VPNs
to complicated steganographic systems.
Our goal is the development of an experiment
to test the usability of such tools.
We focus on one particular system,
Tor Browser, which bundles a variety of circumvention
tools designed for different use cases.

@@

\subsection{Overview} 
Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
how fast a particular task was completed, etc.) throughout the duration of this experiment.

Each session of 30 participants will be placed in the same simulated censorship environment. 
We start off the experiment by informing our participants that they are in an adversarial setting, 
where some websites are blocked while other websites are not. We will instruct them to visit a censored
website and a non-censored website to illustrate that their devices and the network is fully functional and
operating as expected, but that they are in a censorship environment where some websites will fail to load. 
We will take a moment to explain what Tor is, how it is generally used in this case, and ask them to complete 
the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
configuration settings for the country they are simulated to be in.

@@

\subsection{Censorship Environment Simulation}
\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thusly require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

\section{Related Work} %%%

@@

\subsection{Usable Security and User Behavior}
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

@@

\subsection{Experiment Overview}
{\color {red} Talk about how the experiment was for an average user. We start
with the cognitive walkthrough, then have them do one on a dummy
and calibration task, we give feedback on the walkthrough, and then 
give them the freedom to complete the web tasks.}

After the calibration task, we asked participants to complete
the following Tor Browser--related tasks:
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Download Tor (the web browser)
\item Install Tor
\item Check that Tor is working
\item Do a web search for ``onions''
\item Find a YouTube video for ``Ode to Joy''
\item Use ``New Identity'' under the onion menu
\item Explain your best understanding of all the items in the toolbar
\end{enumerate}
We originally had another step after Step~1, ``Configure Tor.''
We removed it after the first two participants
when it became clear that the wording was confusing.
The two main buttons in the configuration wizard are labeled
``Connect'' and ``Configure''; we did not intend for users
to have to go through the longer ``Configure'' path,
but they assumed they had to because of the presence
of the word ``Configure'' in the list of tasks.

@@

\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}

@@

\noindent Subtitled screen videos:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

\section{Exit Survey Questions}
\label{sec:survey} 
\indent \indent Our participants will be taking the following survey, hosted online at 
\url{http://www.surveygizmo.com/s3/2085559/Tor-Usability-Survey/SG_TEST_RUN}.\\

>>>>

\section{Introduction}

@@

@@

{\color {red} what we want to contribute to the research community.}

@@

\subsection{Overview} 
Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
or how fast a particular task was completed) throughout the duration of this experiment.

Each session of 30 participants will be placed in the same simulated censorship environment. 
We start off the experiment by informing our participants that they are in an adversarial setting, 
where some websites are blocked while other websites are not. We will instruct them to visit a censored
website and a non-censored website to illustrate that their devices and the network is fully functional and
operating as expected, but that they are in a censorship environment where some websites will fail to load. 
We will take a moment to explain what Tor is, how it is generally used in this case, and ask them to complete 
the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
configuration settings for the country they are simulated to be in.  Figure ~\ref{dialog} shows one of the 
Tor configuration dialog screens that a user will need to navigate.

@@

\subsection{Censorship Environment Simulation}

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{configuration-dialog.png}
\caption{The fourth and final window of the Tor configuration dialog is what users will use to 
configure their network settings to circumvent censorship. The instructions asks users to 
choose a pluggable transport or enter custom bridges.}
\label{dialog}
\end{figure}

\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thusly require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

\section{Related Work}

@@

\subsection{Usable Security and User Behavior} %%%
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

@@

\subsection{Experiment Overview}
\indent \indent Our experiment consisted of three parts. We first prepare our participants to perform a 
cognitive walkthrough, ask our participants to perform a list of Internet browsing 
tasks while performing a cognitive walkthrough, and finish with an exit survey to collect 
additional information.

To first ensure that our users knew what a cognitive walkthrough is, we explain what a cognitive
walkthrough and give a demonstration of a cognitive walkthrough on a non-related dummy task 
(drawing a red hexagon in the computer graphics program Paint). We then ask our users to perform
an unrelated Internet-based task (finding the population of Zimbabwe) using any browser of their choice
while performing a cognitive walkthrough along the process of completing the task. We give our 
participants feedback on how to properly conduct a cognitive walkthrough ~\cite{wharton1994cognitive}.
This process was also used to get users comfortable with talking our loud with the researcher and gauge 
how comfortable users were with a computer.

Then our participants were instructed to complete the following tasks while performing a cognitive
walkthrough:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Search for, download, and install Tor Browser
\item Do a web search for ``onions'' 
\item Watch an ``Ode to Joy'' video on youtube 
\item Use ``New Identity"
\item Interact with and describe what you think the browser toolbar buttons do
\end{itemize}

The first task was to  test how easy it was for a user to search for, download, and install Tor Browser correctly for use. Since no software is useful if the user is not able to access it, we included this in the list of tasks.
Additionally, we provided three tasks which highlights Tor's ``irregular'' behavior comparatively to other
web browsers, to gauge if users were confused at the non-Google search engine, slow loading
times for videos, and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.

We finished the experiment with a short exit survey which asked their basic demographics information 
such as their age, gender, and education. Upon finishing the survey, participants had the opportunity to 
ask any questions about the Tor Browser that they encountered during their walkthrough.

@@

@@

\noindent We transcribed the audio files from our participants' cognitive walkthroughs
and synced them to the screen capture we took during the duration of the experiment:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

\section{Exit Survey Questions}
\label{sec:survey} 
\indent \indent Our participants will be taking the following exit survey, hosted through
SurveyGizmo at: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{http://www.surveygizmo.com/s3/2085559/Tor-Usability-Survey/SG_TEST_RUN}.
\end{itemize}
